\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach

### 2022-03-20 presentations/presentationBoston/presentationBoston.Rmd
Adds word lists sizes

### Our neutral words (examples, full list size = ADD)

@@

### Our human-related words (examples, full list size = ADD)

switch, studio, stick, soup, sometimes, signal, prior, plant, photo, path, park, near, menu, latter, grass, clock,  wear, walk, visitor, toy, tissue, throw, talk, speak, sleep, eye, enjoy, blogger, character, candidate, breakfast, supper, dinner,
eat, drink, carry, run, cast, ask, awake, ear, nose, lunch

>>>>

### Our neutral words (examples, full list size = 242)

@@

### Our human-related words (examples, full list size = 27)

wear, walk, visitor, toy, tissue, throw, talk, speak, sleep, eye, enjoy, blogger, character, candidate, breakfast, supper, dinner, eat,
drink, carry, run, cast, ask, awake, ear, nose, lunch
